\documentclass[12pt,a4paper]{MKResume}
\author{Mohamed Khalil Ibrahim Eldesoki}
\name{Mohamed Khalil Ibrahim Eldesoki}
\tagline{Senior Software Engineer}
\contactinfo{
    \email{eng.m.5alil@gmail.com}\\
    \phone{+20 1097295321}\\ 
    \phone{+20 1122276787}\\
    \linkedin{in/m-khalil-ibrahim}\\
    \github{M5alil}\\ 
    \location{Fayoum, Egypt}
}

\bio{
    Software developer with 6 years of experience,
    specializing in engineering business solutions. 
    I have successfully implemented industry-standard solutions 
    such as DevOps CI/CD and unit testing.
    My work often involves revitalizing legacy systems over 15 years old,
    enhancing their functionality to meet modern business needs.
    I am a self-learner who adapts quickly and effectively to new challenges.
}
\def\jobs{
    \job{FlairsTech}{Senior software developer}{July 2023 \-- Present}{Maadi, Cairo}{
        Working with FlairsTech has given me the opportunity to work with great organizations around
        the world like Boston Scientific (BSC). With BSC I am a part of a team that works in the medical devices industry.
        And I support designing device system software, and other software that relates to the medical system provided
        by BSC.}
    \job{Zamil Steel}{Senior system engineer}{June 2018 \-- July 2023}{Maadi, Cairo}{
        I was a part of a team that is responsible for making and maintaining systems for the company,
        that provided multiple solutions regarding communication documents,
        and engineering processes like design, detailing, drawings,
        and fabrication. I~was responsible for:
        \begin{itemize}[leftmargin=1.5em,labelsep=0.5em,noitemsep]
            \item maintaining legacy software that search in standard engineering drawings database.
            \item developing new plugins on Tekla Structures that help detailers save time and
                  keep them in standard details.
            \item giving training to various companies' offices for using company's systems.
            \item assisting in developing new software to help with project transformation to
                  Revit.
        \end{itemize}
    }
    \job{Freelance}{Computaional geometry developer}{2020}{remote}{working with web technologies in the computational geometry field.}
}

\def\educations{
    \educationClass{Egypt-Japan University of Science and Technology (EJUST)}{Masters of Business Administration (MBA)}{2023 \-- Present}
    \educationClass{Information Technology Institute (ITI)}{Diploma, AEC Informatics technologies}{2017 \-- 2018}
    \educationClass{Fayoum University, Faculty of engineering}{Bachelor of Engineering}{2009 \-- 2014}
}
\begin{document}
\introSection{}
\bioSection{}
\begin{experience}
    \jobs{}
\end{experience}
\begin{education}
    \educations{}
\end{education}
\begin{skills}
    \begin{tabular*}{\linewidth}[t]{r l}
        \textbf{Languages:}&{\csharp, \Cpp, Javascript, Typescript, Python}\\
        \textbf{Tools:}&{Git, TFVC, Visual studio}\\
        \textbf{Libraries:}&{EFCore, Sqlite, WPF, MVC, RxJS, Rx.NET, Three Js}\\
        \textbf{Areas of Interest:}&{DDD, Backend development, OAuth and Identity management, }
    \end{tabular*}
\end{skills}
\begin{projects}
    \begin{itemize}[leftmargin=0.5em,labelsep=0em]
        \setlength\itemsep{0em}
        \item \textbf{Search Engine for E-Dirve:}
        Maintained MFC \Cpp{} legacy application, adding new functionality.
        \item \textbf{ZS-Connection:}
        Resolved bugs in steel design reports.
        \item \textbf{Tekla plugins:}
        Developed new plugins for Tekla Structures to ensure compliance with company standards.
        \item \textbf{Zamil framing tools:}
        Created backend domain logic and UI for an application that inserts multiple connections and frames.
        \item \textbf{Drawing Creator:}
        Refactored and solved issues in a legacy tool for creating detailed steel drawings.
        \item \textbf{Design to detailing:}
        Presented automation ideas to bridge the gap between design and detailing teams.
        \item \textbf{TeklaToRevit:}
        Developed software to overcome limitations of IFC standards based on company needs.
        \item \textbf{Eduka AB3D (freelance):}
        Modernized and migrated a 3D solver to the web, enabling prediction of 3D shapes from 2D projections.
    \end{itemize}
\end{projects}
\end{document}

